Selective electroporation of the viral envelope

### 2021-04-14 documents/pure_electroporation.tex
relatively consistent convergence!
fft subtratction
Using a real optimal control software
Some work on the paper wording

	Dielectric properties apparently due to the

@@

\lettrine{A}{s} a followup to a technical report \cite{notes2021}, presenting experimental data on protein capsid adjacent technique;

@@

While both mechanisms time constants, those discussed in the previous paper referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging and ion diffusion. The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.

Electroinsertion of proteins into membranes\cite{Clinical1996}; to provoke a local immune response near affected tissues,

@@

@@

As in the previous paper, we must stress that meaningful bioelectrics research hinges very strongly on experimental design and methodology, and very few results can be trusted implicitly.

@@

Note that, mostly contrary to these observations, it is not unambiguously

Note that, despite clear evidence in nanosecond review, microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, a review of in vivo data has not yet found any evidence demonstrating electroporation via pulsed RF.

@@

On the other hand, the human "structome" also contains countless lipid vesicles that might plausibly

@@

Several groups have discussed optimizing

@@

This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of optimal control.

>>>>

	fortuitous Dielectric properties apparently due to the

@@

\lettrine{A}{s} an addendum to a technical report \cite{notes2021} by the author presenting experimental data on protein capsid adjacent technique;

@@

While both mechanisms hinge on time constants, those discussed in the previous paper referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes. The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.

The breakdown of lipid membranes has proved to be an From initial studies of crude membrane breakdown effects \cite{Reversible1979}

"...hit them [cells] with an electric field strong enough to knock over a horse, and they do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."

It is, in general, something of a singular outlier in that it is one of very few biological mechanisms relevant at practical electric field intensities. It also something like integration, which is

Electroinsertion of proteins into membranes\cite{Clinical1996}; to provoke a local immune response near diseased tissues,

@@

The idea of inactivating viruses via electric fields is not new. Very recently, Osorio \cite{Receptor2021} have reported on a susceptibility of SARS-CoV-2's spike proteins to intense electric fields; however, in general, techniques targeting proteins appear to require truly extreme; in their study, fields of up to 2.9 GV/m were required. Dissocation of capsid proteins has been predicted by Man \cite{Picosecond2016b} at 2 GV/m. Similar techniques Tsen \cite{Studies2014}, but these have not been replicated \cite{No2011}. These regimes of intensity may possibly be accessible via ultrashort optical techniques.

@@

As in the previous paper, we must stress that meaningful bioelectrics research hinges very strongly on experimental design and methodology, and very few results can be trusted implicitly. It appears to be very difficult to unambiguously determine cause and effect on a system as complex as a cell; especially when electrodes are in contact with solution and may release an energy-dependent dose of metal ions.

@@

Note that, despite clear evidence in nanosecond review, microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review of vivo data regarding non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation. has not yet found any evidence demonstrating electroporation via pulsed RF. de Seze,

@@

On the other hand, the cellular "structome" also contains countless lipid vesicles that might plausibly be damaged; small pockets of lipid in the endoplasmic reticula, Much like in drug discovery, we do not believe we can meaningfully predict all possible off-target effects.

@@

The question of optimizing a pulse is not novel, having been discussed by many groups in the past. Retelj use a series of

@@

This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of optimal control. In many cases, the optimal control is equal to the transfer function

The time-domain response can be obtained by the convolution integral with the step or impulse response function, or by manually integrating the differential equation via some integrator.
